%====================
% Objective Statement
%====================

\begin{center}
\textbf{Electrical engineer and research coordinator with experience in hardware design for high-speed digital communication, photonic systems, and academic research processes for geophysical science applications.}
\end{center}

\setlength{\parindent}{1.5em}
My background includes avionics sensor design at Amazon, signal integrity engineering at Microsoft, and academic research coordination for geophysics and environmental sensing groups at the University of Washington. I am interested in experimental design workflows, precision measurement systems, and field operations for high-quality scientific data collection. 

I am seeking roles in applied research and instrumentation alongside future graduate study at the intersection of hardware engineering, experimental physics, and geophysical sciences.
\vspace{8pt}

%====================
% EDUCATION
%====================

\section{Education}

\subsection{{Bachelor of Science in Electrical Engineering \hfill August 2015 --- May 2019}}
\subtext{University of Illinois at Urbana--Champaign \hfill Urbana, IL}
\begin{zitemize}
    \item Technical University of Denmark, Exchange Semester (2017)
    \item GE Global Research Internship (2016, 2017) and Amazon Internship (2018)

\end{zitemize}

%====================
% TECHNICAL EXPERIENCE
%====================

\section{Technical Experience}

%====================
% EXPERIENCE A
%====================
\subsection{{Research Coordinator (Photonics) \hfill May 2024 --- May 2025}}
\subtext{University of Washington, College of the Environment \hfill Seattle, WA}
\begin{zitemize}
    \item Supported deployment, operation, and maintenance of photonics-based Distributed Acoustic Sensing (DAS) and data acquisition systems for seismic, oceanic, and cryospheric research.
    \item Coordinated technical activities with external research partners and funding agencies.
    \item Acted as operational liaison between research groups and departmental administration by managing procurement, inventory, shipping, customs documentation, and field logistics.
    \item Supported safety planning and permitting for remote field deployments and instrumentation campaigns.
    \item Developed and maintained experimental workflows for large-volume data management, metadata documentation, and technical reporting across multi-institution collaborations.
    \item Maintained project websites and supported data dissemination platforms.
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Hardware Engineer II (Signal Integrity) \hfill Sept 2021 --- Sept 2023}}
\subtext{Microsoft, Cloud AI Hardware and Advanced Signal Engineering \hfill Seattle, WA}
\begin{zitemize}
    \item Modeled and analyzed end-to-end signal integrity performance across FPGA die, packages, connectors, and board-level interconnects.
    \item Conducted high-speed hardware validation and SI characterization for enterprise AI and cloud infrastructure platforms.
    \item Performed electromagnetic and circuit-level simulations using tools such as ANSYS HFSS and Keysight ADS.
    \item Supported board-level stackup design, routing constraints, and interference mitigation strategies.
    \item Executed laboratory measurements, including S-parameters and eye-diagram analysis, using VNA and time-domain methods.
    \item Collaborated with electrical, mechanical, and systems engineering teams to resolve SI and system integration issues.
    \item Supported contract PCBA design reviews and monitored progress through manufacturing readiness.
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{Hardware Design Engineer (Satellite Avionics) \hfill Apr 2020 --- Sept 2021}}
\subtext{Amazon, Project Kuiper \hfill Seattle, WA}
\begin{zitemize}
    \item Supported early-phase (pre-PDR) satellite avionics sensor subsystem design and development.
    \item Authored design review documents and test validation for electrical, thermal, and mechanical performance.
    \item Defined early avionics sensor requirements from component to system level.
    \item Designed and reviewed schematics, PCB layouts, and housings for sensor prototypes.
    \item Performed board bring-up, debugging, and validation.
    \item Supported hardware radiation test campaigns.
\end{zitemize}

%====================
% EXPERIENCE D
%====================
\subsection{{Technical Program Manager (Robotic Automation Prototypes) \hfill Jul 2019 --- Apr 2020}}
\subtext{Amazon, Worldwide Technical Engineering Services \hfill Seattle, WA}
\begin{zitemize}

    \item Supported nationwide deployment of PLC-based robotic automation prototypes across fulfillment centers.
    \item Managed schedules, logistics, and readiness planning for pilot programs.
    \item Coordinated on-site installations, commissioning, and documentation with engineering and operations teams.
    \item Tracked development milestones through production and operational handoff.
    \item Supported standardization of risk reviews and vendor evaluations.

\end{zitemize}

%====================
% SKILLS
%====================

\section{Skills}

\renewcommand{\arraystretch}{1.2}

\begin{tabularx}{\linewidth}{p{3.2cm} X}

\skills{Communication} &
\textbf{English} (native), Spanish (A2), French (beginner) \\

\skills{Programming} &
Python, C/C++, MATLAB, JavaScript, \LaTeX, Markdown \\

\skills{Development} &
Git, Jupyter, Linux (Bash/Shell), microcontrollers, ArcGIS, Docker, HW/SW RAID storage, HPC remote systems \\

\skills{Instrumentation} &
Distributed Acoustic Sensing (DAS), data acquisition systems (DAQ), noise characterization, sensor calibration, signal integrity analysis, channel simulation, schematic design, PCB layout \\

\skills{Field Operations} &
Hands-on instrumentation system field deployments, logistics coordination, remote system monitoring, experimental test planning, data management, technical documentation \\

\end{tabularx}

%====================
% ACTIVITIES
%====================

\section{Activities}

%====================
% PROFESSIONAL AFFILIATIONS & CERTIFICATIONS
%====================

\subsection{{Professional Affiliations \& Certifications}}
\begin{zitemize}
    \item American Mountain Guides Association (AMGA) Professional Member
    \item American Alpine Club (AAC) Member
    \item Boeing Alpine Society (BOEALPS) Member
    \item Wilderness First Responder (WFR) with AED and CPR Certification\\ 
        {\footnotesize \textit{ National Outdoor Leadership School (NOLS) - December 2025, Yosemite, CA}}
    \item AIARE 1 Avalanche Training Certification\\
        {\footnotesize \textit{ Skyward Mountaineering - December 2025, Silverton, CO}}
    \item Avalanche Companion Rescue Training\\
        {\footnotesize \textit{ SheJumps - January 2025 (Snoqualmie, WA)}}
    \item Washington State Rare Plant Monitor
\end{zitemize}

%====================
% FIELD & ALPINE ACTIVITIES
%====================

\subsection{{Field \& Alpine Activities}}
\begin{zitemize}
    \item Alpine climbing, skiing, and cross-training; prospective AMGA Alpine Guide
    \item SnowGoat Skimo Volunteer for Vertfest and Wy'Easter sanctioned ski mountaineering races
    \item Experience planning safety, navigation, logistics, and remote system management for field exploration in diverse environments
\end{zitemize}

%====================
% CONFERENCES & WORKSHOPS
%====================

\subsection{{Conferences \& Workshops}}
\begin{zitemize}
    \item BOAT Ocean Acoustics Workshop, University of Washington (2025)  
    Two-day intensive workshop on ocean acoustics theory and experimental practice
    \item DesignCon, Santa Clara, CA (2022)  
    Industry conference on high-speed signal integrity, measurement-driven hardware, and PCB manufacturing
\end{zitemize}
